\section{Evaluation}

Over the years, different techniques have been applied for preprocessing, model development, and annotation. Machine learning approaches have been widely used. Deep learning techniques are gradually replacing them and becoming more successful to detect medication names and ADR events.

For ADR classification, among the machine learning-based models, Jonnagaddala et al.~\cite{jonnagaddala2016binary}, in their binary classification, managed to achieve an F-score of 0.33. Meanwhile, Zhang et al.~\cite{zhang2016ensemble}'s ensemble method obtained an F-score of 0.4182 and Sarker et al.~\cite{sarker2016social}'s ensemble method obtained an F-score of 0.46.  Huynh et al.~\cite{huynh2016adverse} compared their deep learning-based model against Zhang et al.~\cite{zhang2016ensemble}’s model. On twitter dataset, their~\cite{huynh2016adverse} model achieved an F-score of 0.51, 0.51, 0.49, and 0.49 using CNN, CRNN, RCNN, and CNNA respectively compared to baseline model's 0.40 F-score. On an unbalanced dataset, Lee et al.~\cite{lee2017adverse}'s Semi-Supervised CNN model for ADR classification outperforms the state-of-the-art supervised ADR classifier from previous work~\cite{sarker2015portable} by +9.9\%. Wu et al.~\cite{wu2019msa} compared their MSA model with Lee et al.~\cite{lee2017adverse}. On a twitter dataset, where Lee et al.'~\cite{lee2017adverse}s model achieved an F-score of 0.503, Wu et al.~\cite{wu2019msa} managed to obtain 0.524. However, Alimova et al.~\cite{alimova2017automated} showed that it's possible to achieve better results using machine learching techniques compared to neural networks when the model is feature-rich. On a twitter dataset, their model~\cite{alimova2017automated} achieved an F-score of 0.702 using SVM and 0.737 using LR against a CNN baseline which achieved 0.702.

Meanwhile, on the research of detecting medication names, Jimeno-Yepes et al.~\cite{jimeno2015identifying} achieved an F-score of 0.65 on a corpus of 1300 tweets using a method based on conditional random fields. Wu et a.~\cite{wu2018detecting} achieved an F-score of 0.9183 using their MSA model on a balanced dataset. Weissenbacher et al.~\cite{weissenbacher2019deep} obtained an F-score of 0.788 on an extremely unbalanced dataset (98959 tweets, with only 0.26\% mentioning medications) and 0.937 on a balanced dataset(50-50 corpus of 15005 tweets) using deep learning methodologies.